Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI$\,$837: A Young Validated Planet in IC~2602

### 2020-07-25 paper/ms.tex
update manuscript
Co-authored-by: George Zhou <george.zhou@cfa.harvard.edu>
make photometry MRT
tweak abstract

%
% TODO:
% * gammadot second method check
%

@@

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry
  from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS,
  and Veloce.  We find that TOI$\,$837 is a $T=9.9$ mag
  G0/F9 dwarf in the southern open cluster IC 2602.  The star
  and planet are therefore $35^{+11}_{-5}$ million years old.
  Combining the transit photometry with a prior on the stellar
  parameters derived from the cluster color-magnitude diagram, we find
  that the planet has an orbital period of $8.3\,{\rm d}$ and is
  slightly smaller than Jupiter ($R_{\rm p} = 0.80^{+0.09}_{-0.03}
  \,R_{\rm Jup}$).  The transits are either grazing or nearly grazing.
  From radial velocity monitoring, we limit the minimum mass to less
  than 1.20 $M_{\rm Jup}$ (3-$\sigma$).  Grazing transits are a cause
  for concern, as they are usually indicative of astrophysical false
  positive scenarios.  Our follow-up data show that such scenarios are
  highly unlikely.  Our combined multi-color photometry,
  high-resolution imaging, and radial velocities rule out hierarchical
  eclipsing binary scenarios.  Background eclipsing binary scenarios,
  though limited by speckle imaging, formally remain a 0.2\%
  possibility.  TOI 837.01 is therefore a validated adolescent
  exoplanet.  Further observations of its stellar obliquity,
  atmosphere, and mass should confirm its planetary nature beyond
  doubt, and could improve our understanding of how the physical and
  orbital properties of exoplanets change in time.
\end{abstract}

@@

\subsubsection{FEROS}
TOI 837.01 was monitored with the FEROS echelle spectrograph
\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2$\,$m
telescope at the ESO La Sille Observatory, in Chile. FEROS has a
resolution of $\approx$48,000 across a spectral range of 350–920 nm.
It has a remarkably high efficiency of $\approx$20\%. We obtained 13
spectra of \tn\ between July 5 of 2019 and March 14 of 2020 in the
context of the Warm gIaNts with tEss (WINE) collaboration, which
focuses on the systematic characterization of TESS transiting giant
planets with moderately long orbital periods \citep[{\it
e.g.},][]{brahm:2019,jordan:2020}.  We adopted exposure times of 500
and 600 seconds and the observations were performed with the
simultaneous calibration mode for tracing the instrumental velocity
variations with a comparison fiber illuminated with a ThAr lamp. FEROS
data was processed with the \texttt{ceres} pipeline
\citep{brahm_2017_ceres}, which delivers precision radial velocities
and bisector span measurements through cross-correlation of the
extracted spectra with a binary mask resembling the properties of a
G2V star. The radial velocities are given in Table~\ref{tab:rvs}, and
shown in Figure~\ref{fig:followup}.

>>>>

@@

\begin{abstract}
  We report the discovery of TOI 837.01 and its validation as a
  transiting planet.  We characterize the system using data from the
  NASA TESS mission, the ESA Gaia mission, ground-based photometry
  from El Sauce and ASTEP400, and spectroscopy from CHIRON, FEROS, and
  Veloce.  We find that TOI 837 is a $T=9.9$ mag G0/F9 dwarf in the
  southern open cluster IC 2602.  The star and planet are therefore
  $35^{+11}_{-5}$ million years old.  Combining the transit photometry
  with a prior on the stellar parameters derived from the cluster
  color-magnitude diagram, we find that the planet has an orbital
  period of $8.3\,{\rm d}$ and is slightly smaller than Jupiter
  ($R_{\rm p} = 0.80^{+0.09}_{-0.03} \,R_{\rm Jup}$).  The transits
  are either grazing or nearly grazing.  From radial velocity
  monitoring, we limit $M_{\rm p}\sin i$ to less than 1.20 $M_{\rm
  Jup}$ (3-$\sigma$).  Grazing transits are a cause for concern, as
  they are often indicative of astrophysical false positive scenarios.
  Our follow-up data show that such scenarios are highly unlikely.
  Our combined multi-color photometry, high-resolution imaging, and
  radial velocities rule out hierarchical eclipsing binary scenarios.
  Background eclipsing binary scenarios, though limited by speckle
  imaging, formally remain a 0.2\% possibility.  TOI 837.01 is
  therefore a validated adolescent exoplanet.  The planetary nature of
  the system can be confirmed or refuted through observations of the
  stellar obliquity or the planetary mass.  Such observations may also
  improve our understanding of how the physical and orbital properties
  of exoplanets change in time.
\end{abstract}

@@

\subsubsection{FEROS}
TOI 837.01 was monitored with the FEROS echelle spectrograph
\citep{kaufer_commissioning_1999}, mounted on the MPG 2.2$\,$m
telescope at the ESO La Sille Observatory, in Chile. FEROS has a
resolution of $\approx$48,000 across a spectral range of 350–920 nm.
It has a remarkably high efficiency of $\approx$20\%. We obtained 13
spectra of \tn\ between July 5 of 2019 and March 14 of 2020 in the
context of the Warm gIaNts with tEss (WINE) collaboration, which
focuses on the systematic characterization of TESS transiting giant
planets with moderately long orbital periods \citep[{\it
e.g.},][]{brahm:2019,jordan:2020}.  We adopted exposure times of 500
and 600 seconds and the observations were performed with the
simultaneous calibration mode for tracing the instrumental velocity
variations with a comparison fiber illuminated with a ThAr lamp. FEROS
data was processed with the \texttt{ceres} pipeline
\citep{brahm_2017_ceres}, which delivers precision radial velocities
and bisector span measurements through cross-correlation of the
extracted spectra with a binary mask resembling the properties of a
G2V star. The radial velocities are given in Table~\ref{tab:rvs}, and
shown in Figure~\ref{fig:followup}.
To check for the presence of secondary lines, we performed a similar
injection-recovery exercise as with the CHIRON data. 
We achieved slightly worse limits, likely due to the lower spectral
resolution of FEROS, and therefore adopted the CHIRON limits.
